---
title: "Auto-Gaze Data Processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, 
                      message = F, fig.width = 6, 
                      fig.asp = 0.63)
```

```{r}
library(magrittr); library(tidyverse); library(here)
data_path_read <- "data/soc_ref/ground_truth/01_raw"
data_path_write <- "data/soc_ref/ground_truth/02_processed"
features_path <- "data/soc_ref/open_face_output"
theme_set(ggthemes::theme_few())
```

Read and merge separate gold code files using purrr map. 

```{r}
files <- list.files(here::here(data_path_read))

# indexing is a hacky way to separate the ground truth coding files from the timing df
d <- files[1:4] %>% map_dfr(~ read_csv(file.path(here::here(data_path_read, .))))
d_timing <- read_csv(here::here(data_path_read, files[5]))

# read in open face model output
d_features <- read_csv(here::here(features_path, "results_openFace_03_3_18.csv")) %>% 
  select(frame:gaze_angle_y, pose_Tx:pose_Rz)
```

Join gold code with new features and select just the gaze relevant features.

```{r}
d_features %<>% left_join(., select(d, timestamp, gold_code), 
                          by = c("timestamp"))
```

### Add trial timing information to features.

```{r}
d_timing %<>% 
  mutate(phase_onset_sec = phase_onset / 1000,
         phase_offset_sec = phase_offset / 1000)
```

Round the timestamp to make it easier to join the human coded timing information.

```{r}
d_features %<>% mutate(timestamp_rounded = round(timestamp, 1))
```

```{r}
timing_human <- d_timing$phase_onset_sec %>% unique()
timing_openface <- d_features$timestamp_rounded %>% unique()
intersect(timing_human, timing_openface) 
setdiff(timing_human, timing_openface) 
```

Create long version of trial timing information where we interpolate between the start and end of
phase markers.

```{r}
# takes in a trial with information about the phase onset and offset
# return the interpolated timing dataframe with a column for timestamps linked to phase information
add_phase_timing <- function(df_trial, df_feats) {
  start <- df_trial %>% pull(phase_onset_sec)
  end <- df_trial %>% pull(phase_offset_sec)
  
  df_feats %>% 
    filter(timestamp_rounded >= start, timestamp_rounded <= end) %>% 
    select(timestamp)
}
```

Some purrr::map magic to apply the add_phase_timing function to subsets of our dataset, i.e., each trial and phase. 

```{r}
d_timing_nested <- d_timing %>% 
  group_by(trial, phase, num_looks, condition) %>% 
  nest()

d_timing_nested %<>% 
  mutate(timing = map(data, .f = add_phase_timing, df_feats = d_features)) %>% 
  unnest(timing) # pull out the timing information 

## Join the trial timing and num looks information with gaze features
d_features %<>% left_join(., d_timing_nested, by = "timestamp") 
```

Plot phase timing for a couple of trials to make sure things looks reasonable. 

```{r}
d_features %<>% 
  filter(!is.na(trial), str_detect(trial, pattern = "t")) %>% 
  mutate(trial = str_extract(trial, pattern = "[[:digit:]]+") %>% as.numeric()) 
  
d_features %>% 
  ggplot(aes(x = timestamp, y = phase)) +
  geom_line(size = 2) +
  labs(x = "time (sec)") + 
  facet_wrap(~trial, scales = "free_x") +
  guides(color = F)
```

todo: check with emily to see if these timings look correct.

### Write to disk

```{r}
write_csv(d_features, here::here(data_path_write, "ground_truth_processed_tidy.csv"))
```
